---
title: "linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package lets you fit a linear regression model using ordinary least squares.
You create the model with the function `linreg()`, and the result is an object
with methods for printing, plotting and inspecting the fit.

This vignette goes through how the package works, what is available and how to
use it, with the `iris` dataset as an example.

## Data

`iris` is a built in dataset with measurements of 150 flowers from three species.
In the examples we model petal length (`Petal.Length`) using species (`Species`).

```{r setup}
library(Lab4PKG)
data(iris)
head(iris)
```

## Fitting a model

`linreg()` takes a formula and a data frame.

```{r}
estimation <- linreg(Petal.Length ~ Species, data = iris)
```

## Methods

### print()

Prints the call and the estimated coefficients. Since the class also has a
`show()` method, just typing `estimation` gives the same output.

```{r}
estimation$print()
```

### plot()

Creates two plots with ggplot2. *Residuals vs Fitted* shows whether the
residuals are spread evenly around zero, and *Scale-Location* shows whether
the spread of the residuals changes with the fitted values. The red line
connects the median at each fitted value.

```{r}
estimation$plot()
```

### resid()

Returns the residuals, the difference between the observed and the fitted values.

```{r}
head(estimation$resid())
```

### pred()

Returns the fitted values.

```{r}
head(estimation$pred())
```

### coef()

Returns the estimated coefficients as a named vector.

```{r}
estimation$coef()
```

### summary()

Prints a table with the estimated coefficients, their standard errors,
t values and p values. Stars mark significance (`***` p < 0.001,
`**` p < 0.01, `*` p < 0.05). Below the table it prints the residual
standard error and the degrees of freedom.

```{r}
estimation$summary()
```
